Slavnov products and KP tau functions

### 2025-04-16 draft.tex
calculate the ba function -- probably wrong

It is easy to show, see~\cite{Araujo:2021ghu} and references therein,
that that the tau function~(\ref{eq:tau-function}) admits an integral
representation of the form
\begin{equation}
  \label{eq:tau-function-miwa}
  \bm{\tau}(\bm{t}, \bm{v}) =
    \det_{j,k}\left(
    \oint_{\gamma_k} \frac{d w}{2\pi i} e^{\xi(\bm{t}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k} \; ,
    \right)
\end{equation}
where 
\begin{equation}
  \xi(\bm{t}, w^{-1}) = \sum_{p=1}^\infty t_p w^{-p} \quad \Leftrightarrow \quad
  \xi(\bm{z}, w^{-1}) = w^n \prod_{j=1}^n (w - z_j)^{-1} \; ,
\end{equation}
and the integration contour \(\gamma_k\) encloses all points
\(\{z_j\}_{j=1}^n\) but avoids the Bethe root \(v_k\).
One of the advantages of this representation is
that now it makes sense to consider the limit of the infinite chain,
\(n\to \infty\).

@@

Using these expressions, we can write 
\begin{equation}
  \bm{\tau}(\bm{t} - [\lambda^{-1}], \bm{v}) =
  \det_{j,k}\left[
  \oint_{\gamma_k} \frac{dw}{2\pi i} e^{\xi(\bm{t}, w^{-1})} \left( 1 - \frac{1}{\lambda w} \right) \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k} 
  \right]\; .
\end{equation}
Now, we define the matrix \(\widetilde{\mathcal{K}}(\lambda)\) by its components
\begin{equation}
    \widetilde{\mathcal{K}}_{jk}(\lambda)  = -  \frac{1}{\lambda} 
  \oint_{\gamma_k} \frac{dw}{2\pi i} e^{\xi(\bm{t}, w^{- 1})} \frac{w^{-j -1 }\mathcal{Y}_k(w)}{w - v_k} \; ,
\end{equation}
and we then have 
\begin{equation}
  \bm{\tau}(\bm{t} - [\lambda^{-1}], \bm{v}) =
  \bm{\tau}(\bm{t}, \bm{v})
  \det \left( \mathbb{1} +  \mathcal{K}^{-1} \widetilde{\mathcal{K}}(\lambda) \right)\; .
\end{equation}

>>>>

It is easy to show, see~\cite{Araujo:2021ghu} and references therein,
that that the tau function~(\ref{eq:tau-function}) admits an integral
representation of the form
\todo{Zero is not a pole of this expression}
\begin{equation}
  \label{eq:tau-function-miwa}
  \bm{\tau}(\bm{t}, \bm{v}) =
    \det_{j,k}\left(
    \oint_{\gamma_k} \frac{d w}{2\pi i} e^{\xi(\bm{t}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k} \; ,
    \right)
\end{equation}
where 
\begin{equation}
  \xi(\bm{t}, w^{-1}) = \sum_{p=1}^\infty t_p w^{-p} \quad \Leftrightarrow \quad
  \xi(\bm{z}, w^{-1}) = w^n \prod_{j=1}^n (w - z_j)^{-1} \; ,
\end{equation}
and the integration contour \(\gamma_k\) encloses all points
\(\{z_j\}_{j=1}^n\) but avoids the Bethe root \(v_k\).
One of the advantages of this representation is
that now it makes sense to consider the limit of the infinite chain,
\(n\to \infty\).

@@

Using these expressions, we can write 
\todo{Zero is a pole of this expression}
\begin{equation}
  \bm{\tau}(\bm{t} - [\lambda^{-1}], \bm{v}) =
  \det_{j,k}\left[
  \oint_{\gamma_k} \frac{dw}{2\pi i} e^{\xi(\bm{t}, w^{-1})} \left( 1 - \frac{1}{\lambda w} \right) \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k} 
  \right]\; .
\end{equation}
We can now  calculate this integral.

\subsubsection{Regular case}
Let \(D_k\) be a domain defined by \(\partial D = \gamma_k\). We can
see that the function
\begin{equation}
  \widetilde{\mathcal{Y}}_k(w)
  = \left( 1 - \frac{1}{\lambda w} \right) \mathcal{Y}_k(w) \; ,
\end{equation}
is holomorphic in \(D_k\) and has a zero at \(\lambda = z_k^{-1}\). Therefore, we can repeat the previous arguments
to calculate the shifted tau functions. The final result is 
\begin{subequations}
\begin{equation}
  \bm{\tau}(\bm{t} - [\lambda^{-1}], \bm{v})\ \Rightarrow \
  \bm{\tau}(\lambda^{-1};\bm{z},\bm{v}) = 
  \frac{1}{\Delta(\bm{z})}
  \det_{j,k}\left[
  \left( 1 - \frac{1}{\lambda z_j} \right) \frac{\mathcal{Y}_j(z_k)}{z_k - v_j} 
  \right]\; , 
\end{equation}
and elementary column operations, we find
\begin{equation}
  \begin{split}
    \bm{\tau}(\lambda^{-1};\bm{z},\bm{v})
    & = \bm{\tau}(\bm{z},\bm{v}) \prod_{j=1}^n\left( 1 - \frac{1}{\lambda z_j} \right) \\ 
    & = \bm{\tau}(\bm{z},\bm{v}) (-1)^n \prod_{j=1}^n \frac{1 - \lambda z_j}{\lambda z_j} \; . 
  \end{split}
\end{equation}
\end{subequations}

Putting all these facts together, we find that the Baker-Akhiezer function is given by
\begin{equation}
  \psi(\lambda, \bm{z}) =  \frac{(-1)^n}{\lambda^n}\prod_{j=1}^n \frac{1}{z_j}\; ,
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fredholm determinant}

Now, we define the matrix \(\widetilde{\mathcal{K}}(\lambda)\) by its components
\begin{equation}
    \widetilde{\mathcal{K}}_{jk}(\lambda)  = -  \frac{1}{\lambda} 
  \oint_{\gamma_k} \frac{dw}{2\pi i} e^{\xi(\bm{t}, w^{- 1})} \frac{w^{-j -1 }\mathcal{Y}_k(w)}{w - v_k} \; ,
\end{equation}
and we then have 
\begin{equation}
  \bm{\tau}(\bm{t} - [\lambda^{-1}], \bm{v}) =
  \bm{\tau}(\bm{t}, \bm{v})
  \det \left( \mathbb{1} +  \mathcal{K}^{-1} \widetilde{\mathcal{K}}(\lambda) \right)\; .
\end{equation}
